Algomusicology, ?, Profit

### 2016-04-02 paper.tex
Use explanatory-power instead of randomness (as explanatory-power is relative to a particular description and randommness isn't really).

The randomness of a description can be measured by comparing the length of the textual description and the length
of the resulting value. If there is no way to describe a value more concisely than the value itself, we say that it is
random.

\begin{verbatim}
(defmacro randomness [expression]
  `(/ (description-length ~expression)
      (result-length ~expression)))

(fact
  (randomness (repeat 65 \G)) => 13/131)
\end{verbatim}

@@

Using a little more macro magic, we can calculate the ratio between the above description and the literal notes
of the song.

@@

(fact
  (definitional description-length row-row) => 281
  (definitional result-length row-row) => 2037
  (definitional randomness row-row) => 281/2037)
\end{verbatim}

>>>>

The explanatory power of a description can be measured by comparing the length of the textual description and the length
of the resulting value. Explanatory power is the reciprocal of the compression ratio, where representing a value by an
expression is viewed as a compression strategy.

If there is no way to describe a value more concisely than the value itself, we say that it is random. An explanatory
power of one or less is no explanation at all.

\begin{verbatim}
(defmacro explanatory-power [expression]
  `(/ (result-length ~expression)
      (description-length ~expression)))

(fact
  (explanatory-power (repeat 65 \G)) => 131/13)
\end{verbatim}

@@

Using a little more macro magic, we can calculate the ratio between the above description and the literal notes
of the song. The definitional macro allows us to use the symbol row-row in our fact notation, rather than having to
paste in the entire expression.

@@

(fact
  (definitional description-length row-row) => 281
  (definitional result-length row-row) => 2037
  (definitional explanatory-power row-row) => 2037/281)
\end{verbatim}
